Your Title Goes Here

### 2017-12-29 documentation/documentation.tex
stucturing the title page

%% Language and font encodings
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}

% Specify bibliography package
\usepackage{csquotes}% Recommended
\usepackage[style=apa]{biblatex}
\DeclareLanguageMapping{american}{american-apa}

\addbibresource{references.bib}

%% Sets page size and margins
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}
\setlength{\parskip}{1em}

%% package for formatting and highlighting source code
\usepackage{listings}
\usepackage{color}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage[colorlinks=true, allcolors=black]{hyperref}
\usepackage{graphicx}
\usepackage{setspace}

%% packages for tikz diagrams
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

%% styling for tikz diagrams
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=10cm, minimum height=1cm,text centered, text width=10cm, draw=black, fill=gray!10]
\tikzstyle{process} = [rectangle, minimum width=10cm, minimum height=1cm, text centered, text width=10cm, draw=black, fill=orange!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

% Section Title Margins
\usepackage{titlesec}
\titlespacing*{\section}
{0pt}{3.0ex plus 1ex minus .2ex}{0.7ex}
\titlespacing*{\subsection}
{0pt}{1.4ex}{0pt}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3
}

\title{Review of Assigned Readings}
\author{Your Name Goes Here}

    \begin{document}
    \begin{titlepage}
      	\begin{figure}
      	\centering
        \includegraphics[scale=0.35]{logohsg}
        \end{figure}
        \centering
        School of Management, Economics, Law, Social Schiences and International Affairs \par
        \vspace{2.5cm}
        {\huge\bfseries The effect of Twitter activity on
Bitcoin price\par}      
        {\Huge\itshape Documentation\par}
        \vspace{1.5cm}     
        {Software Engineering for Economists \\ (7,610,1.00) \par}
        \vspace{1.3cm}
        {Dimitrios Koumnakes - 10-613-370 \\ Severin Kranz - 13-606-355 \\ Joël Sonderegger - 11-495-488 \\
       	Alen Stepic - 11-475-258 \\Chi Xu - XX-XXX-XXX \par}
        \vspace{1cm}
        Fall Term 2017
        \vfill
        Supervisor
        \linebreak
        Prof. Dr. Philipp \textsc{Zahn}
        \linebreak
        Department of Economics

    % Bottom of the page
     {\centering \today\par}

    \end{titlepage}

    \clearpage
    \tableofcontents

@@

%************************** Bibliography **************************
\printbibliography
\clearpage

>>>>

% Language and font encodings
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}

% Specify bibliography package
\usepackage{csquotes}% Recommended
\usepackage[style=apa]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{references.bib}

% Sets page size and margins
\usepackage[top=2cm,bottom=2cm,left=2cm,right=2cm,marginparwidth=1.75cm]{geometry}
\setlength{\parskip}{1em}

% package for formatting and highlighting source code
\usepackage{listings}
\usepackage{color}

% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage[colorlinks=true, allcolors=black]{hyperref}
\usepackage{graphicx}
\usepackage{setspace}

% packages for tikz diagrams
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

% styling for tikz diagrams
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=10cm, minimum height=1cm,text centered, text width=10cm, draw=black, fill=gray!10]
\tikzstyle{process} = [rectangle, minimum width=10cm, minimum height=1cm, text centered, text width=10cm, draw=black, fill=orange!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

% Section Title Margins
\usepackage{titlesec}
\titlespacing*{\section}
{0pt}{3.0ex plus 1ex minus .2ex}{0.7ex}
\titlespacing*{\subsection}
{0pt}{1.4ex}{0pt}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=3}

\title{Your Title Goes Here}
\author{Your Name Goes Here}

%************************** DOCUMENT_STARTS_HERE **************************
\begin{document}

\begin{titlepage}
	\begin{figure}
	\centering
	\includegraphics[scale=0.32]{logohsg}
	\end{figure}
\centering
\centering
{\scshape\large School of Management, Economics, Law, Social Sciences and International Affairs \par}
\vspace{1.7cm}
{\huge\bfseries The effect of Twitter activity on \\ Bitcoin price\par}
\vspace{1.0cm}
{\Huge\itshape Documentation\par}
\vspace{1.0cm}     
{\Large Software Engineering for Economists \\ (7,610,1.00) \par}
\vspace{1.2cm}
{Alen Stepic - 11-475-258 \\ Dimitrios Koumnakes - 10-613-370 \\ Severin Kranz - 13-606-355 \\ Joël Sonderegger - 11-495-488 \\ Chi Xu - XX-XXX-XXX \par}
\vspace{1.2cm}
Fall Term 2017 \\
\vspace{1.2cm}
{Supervisor\\ Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen\\ Department of Economics\par}
\vspace{0.8cm}
{\centering\today\par}
\end{titlepage}

\tableofcontents

@@

%************************** Bibliography **************************
\section{References}
\printbibliography[heading=none]
\clearpage
